On the performance of the MAC model

### 2018-11-01 2018_nips_vigil/introduction.tex

Many approaches have been explored, 
%although they often appear to struggle on tasks with a structured and compositional nature \citep{hudson2018compositional}.
such as modular structures, resembling the trees of programming languages, that compose neural modules from a fixed predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}. Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also frequently used to guide the focus of the system over the image and the question words.
%Other approaches such as \vm{Ask Tomasz what he is thinking about.}.

>>>>

Many approaches have been explored, 
%although they often appear to struggle on tasks with a structured and compositional nature \citep{hudson2018compositional}.
such as modular networks, that combine modules coming from a predefined collection \cite{andreas2016learning,johnson2017inferring, mascharka2018transparency}. Attention mechanisms (\cite{bahdanau2014neural}, \cite{xu2015show}) are also frequently used to guide the focus of the system over the image and the question words.
%Other approaches such as \vm{Ask Tomasz what he is thinking about.}.
